### 2023-03-28 README.Rmd
updating README

- `R`: contains the simulation and utility functions used in the paper and supplementary materials
- `documents`: contains the `.Rmd` files to reproduce the paper and supplementary materials manuscripts
- `scripts`: contains the script used to produce complex objects and figures
  - `scripts\r-img.R`: create the paper figures. Figures that are not created in this script using `ggplot2` are created with the open-source program [*Inkscape*](https://inkscape.org/) and contained in the `../img/` folders.
- `objects`: contains the result of objects created by the `scripts/` scripts.

>>>>

- `R`: contains the simulation and utility functions used in the paper and the supplementary materials
- `documents`: contains the `.Rmd` files to reproduce the paper and supplementary materials manuscripts
- `scripts`: contains the script used to produce complex objects and figures
  - `scripts\r-img.R`: create the paper figures. Figures that are not created in this script using `ggplot2` are created with the open-source program [*Inkscape*](https://inkscape.org/) and contained in the `../img/` folders.
- `objects`: contains the result of objects created by the `scripts/` scripts.
